\documentclass[journal]{IEEEtran}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)


% *** MISC UTILITY PACKAGES ***
\usepackage{url} % Insert URL addresses within the document
\usepackage[colorlinks=false]{hyperref} % Makes internal and external references to clickable links within the PDF document

% *** GRAPHICS RELATED PACKAGES ***
\usepackage[pdftex]{graphicx} % Basic commands to include graphics

% *** MATH PACKAGES ***
\usepackage{amsmath} % Basic commands to depict math equations
\usepackage{bm} % bold font math symbols

% *** CORRECT REPRESENTATION OF SI UNITS ***
\usepackage{siunitx} 

% *** ALIGNMENT PACKAGES ***
\usepackage{array} % nicer lookig tables and 

% *** TABLE PACKAGES ***
\usepackage{booktabs} % nicer tables
\usepackage{multirow} % multi-row cells in tables



\begin{document}

% Check for correct title
\title{\LARGE{Pintos Project III: Virtual Memory}}

% Insert your name and student ID here
\author{First Name 1 Last Name 1, Student ID 1 \\\and 
        First Name 2 Last Name 2, Student ID 2 \\\and 
        First Name 3 Last Name 3, Student ID 3} 


%%%% Do not change this %%%%
\markboth{CS2S01 Operating Systems 2021}{CS2S01 Operating Systems 2021}
\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Preliminaries}
%%%% Some instruction words (delete this section for your submission) %%%%
If you have any preliminary comments on your submission, notes for the TAs, or extra credit, please give them here.

Please cite any offline or online sources you consulted while preparing your submission, other than the Pintos documentation, course text, lecture notes, and course staff.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Page Table Management}
\subsection{Data Structures}
%%%% Some instruction words (delete this section for your submission) %%%%
A1: Copy here the declaration of each new or changed 'struct' or 'struct' member, global or static variable, 'typedef', or enumeration.  Identify the purpose of each in 25 words or less.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Algorithms}
%%%% Some instruction words (delete this section for your submission) %%%%
A2: Briefly describe what happens in a call to timer\_sleep(), including the effects of the timer interrupt handler.

A3: How does your code coordinate accessed and dirty bits between kernel and user virtual addresses that alias a single frame, or alternatively how do you avoid the issue?
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Synchronization}
%%%% Some instruction words (delete this section for your submission) %%%%
A4: When two user processes both need a new frame at the same time, how are races avoided?


%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Rationale}
%%%% Some instruction words (delete this section for your submission) %%%%
A5: Why did you choose the data structure(s) that you did for representing virtual-to-physical mappings?
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Paging to add from disk}

\subsection{Data Structures}
%%%% Some instruction words (delete this section for your submission) %%%%
 B1: Copy here the declaration of each new or changed `struct' or `struct' member, global or static variable, `typedef', or enumeration.  Identify the purpose of each in 25 words or less.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Algorithms}
%%%% Some instruction words (delete this section for your submission) %%%%
B2: When a frame is required but none is free, some frame must be evicted.  Describe your code for choosing a frame to evict.

B3: When a process P obtains a frame that was previously used by a process Q, how do you adjust the page table (and any other data structures) to reflect the frame Q no longer has?


B4: Explain your heuristic for deciding whether a page fault for an invalid virtual address should cause the stack to be extended into the page that faulted.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Synchronization}
%%%% Some instruction words (delete this section for your submission) %%%%
B5: Explain the basics of your VM synchronization design.  In particular, explain how it prevents deadlock.  (Refer to the textbook for an explanation of the necessary conditions for deadlock.)

B6: A page fault in process P can cause another process Q's frame to be evicted.  How do you ensure that Q cannot access or modify the page during the eviction process?  How do you avoid a race between P evicting Q's frame and Q faulting the page back in?

B7: Suppose a page fault in process P causes a page to be read from the file system or swap.  How do you ensure that a second process Q cannot interfere by e.g. attempting to evict the frame while it is still being read in?

B8: Explain how you handle access to paged-out pages that occur during system calls.  Do you use page faults to bring in pages (as in user programs), or do you have a mechanism for "locking" frames into physical memory, or do you use some other design?  How do you gracefully handle attempted accesses to invalid virtual addresses?
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Rationale}
%%%% Some instruction words (delete this section for your submission) %%%%
B9: A single lock for the whole VM system would make synchronization easy, but limit parallelism.  On the other hand, using many locks complicates synchronization and raises the possibility for deadlock but allows for high parallelism.  Explain where your design falls along this continuum and why you chose to design it this way.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Survey Questions}
%%%% Some instruction words (delete this section for your submission) %%%%
Answering these questions is optional, but it will help us improve the
course in future quarters.  Feel free to tell us anything you
want--these questions are just to spur your thoughts.  You may also
choose to respond anonymously in the course evaluations at the end of
the quarter.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
\item \textit{In your opinion, was this assignment, or any one of the three problems in it, too easy or too hard?  Did it take too long or too little time?}

\item \textit{Did you find that working on a particular part of the assignment gave you greater insight into some aspect of OS design?}

\item \textit{Is there some particular fact or hint we should give students in future quarters to help them solve the problems?  Conversely, did you find any of our guidance to be misleading?}

\item \textit{Do you have any suggestions for the TAs to more effectively assist students, either for future quarters or the remaining projects?}

\item \textit{Any other comments?}
\end{itemize}

\end{document}


